Reading Notes

### 2020-09-14 2pd.tex
fixed table and citations

To improve the useability and extensibility of molecular simulation tools, I have been intentional about incorporating Software Carpentry priniciples into my work\cite{swc}.
My experience as a Software Carpentry instructor has given me the pedagocial foundation to think about how users take in new information.
With these principles in mind, I have created tutorial examples to help current and future students understand scientific concepts and how to use computational tools\cite{notebooktutorials}

@@

\section*{Timeline for Implementation and Evaluation}

\begin{table}[h]
    \resizebox{\columnwidth}{!}{\renewcommand{\arraystretch}{1.1}
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
        \hline
        \multirow{2}{*}{PROJECT TASK}
            &\multicolumn{3}{c}{YEAR 1}
            &\multicolumn{3}{|c}{YEAR 2} 
            &\multicolumn{3}{|c}{YEAR 3} 
            &\multicolumn{3}{|c|}{YEAR 4} 
            &\multicolumn{3}{c|}{YEAR 5}
            &\multicolumn{3}{c|}{YEAR 6} \\ 
        \hhline{~--------------------}
        & 1 & 2 & 3 & 1 & 2 & 3 & 1 & 2 & 3 & 1 & 2 & 3 & 1 & 2 & 3 & 1 & 2 & 3\\
        \hline
        Complete Coursework 
            &\multicolumn{7}{|c|}{{\cellcolor{lgray}}} & & & & & & & & & & &\\
        \hline
        Present at a Conference  
            & & & & & & & x & & & & & & & & & & &\\
        \hline
        Publish a First Author Paper
            & & & & x & & & & & & & & & & & & & &\\
        \hline
        Proposal and Comprehensive Exam
            & & & & & & & & * & & & & & & & & & &\\
        \hline
        Expand Functionality of Open Source Packages 
            & & & & & \multicolumn{12}{|c|}{{\cellcolor{lgray}}} & &\\
        \hline
        Develop Coarse-Graining Package              
            & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
        \hline
        Develop Automated MS IBI Code                
            & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
        \hline
        Develop Backmapping Package                  
            & & & & & & & & & & \multicolumn{6}{|c|}{{\cellcolor{lgray}}}& & &\\
        \hline
        Generate Coarse-Grain Morphologies           
            & & & & & & & & & & & \multicolumn{6}{|c|}{{\cellcolor{lgray}}}& &\\
        \hline
        Evaluate OPV Device Performance 
            & & & & & & & & & & & & \multicolumn{6}{|c|}{{\cellcolor{lgray}}} &\\
        \hline
        Write Dissertation 
            & & & & & & & & & & & & & &\multicolumn{5}{|c|}{{\cellcolor{lgray}}}\\
        \hline
        Present Dissertation Defense  
            & & & & & & & & & & & & & & & & & &{\cellcolor{lgray}}\\
        \hline
    \end{tabular}}\caption{Anticipated timeline. * indicates right now, x indicates already accomplished.}
\end{table}

>>>>

To improve the useability and extensibility of molecular simulation tools, I have been intentional about incorporating Software Carpentry priniciples into my work\cite{swc-main}.
My experience as a Software Carpentry instructor has given me the pedagocial foundation to think about how users take in new information.
With these principles in mind, I have created tutorial examples to help current and future students understand scientific concepts and how to use computational tools\cite{notebooktutorials}

@@

\pagebreak
\section*{Timeline for Implementation and Evaluation}
\begin{table}[h!]
\centering
    \resizebox{\textwidth}{!}{%
\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|}
\hline
\multicolumn{1}{|c|}{} & \multicolumn{3}{l|}{YEAR 1} & \multicolumn{3}{l|}{YEAR 2} & \multicolumn{3}{l|}{YEAR 3} & \multicolumn{3}{l|}{YEAR 4} & \multicolumn{3}{l|}{YEAR 5} & \multicolumn{3}{l|}{YEAR 6} \\ \cline{2-19} 
\multicolumn{1}{|c|}{\multirow{-2}{*}{PROJECT TASK}} & 1 & 2 & 3 & 1 & 2 & 3 & 1 & 2 & 3 & 1 & 2 & 3 & 1 & 2 & 3 & 1 & 2 & 3 \\ \hline
Complete Coursework & \multicolumn{7}{l|}{\cellcolor[HTML]{C0C0C0}} &  &  &  &  &  &  &  &  &  &  &  \\ \hline
Present at a Conference &  &  &  &  &  &  &  & x &  &  &  &  &  &  &  &  &  &  \\ \hline
Publish a First Author Paper &  &  &  & x &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ \hline
Proposal and Comprehensive Exam &  &  &  &  &  &  &  &  & * &  &  &  &  &  &  &  &  &  \\ \hline
Expand Functionality of Open Source Packages &  &  &  &  & \multicolumn{12}{l|}{\cellcolor[HTML]{C0C0C0}} &  &  \\ \hline
Develop Coarse-Graining Package &  &  &  &  &  &  & \multicolumn{8}{l|}{\cellcolor[HTML]{C0C0C0}} &  &  &  &  \\ \hline
Implement Automated MS IBI Package &  &  &  &  &  &  &  &  &  & \multicolumn{5}{l|}{\cellcolor[HTML]{C0C0C0}} &  &  &  &  \\ \hline
Develop Backmapping Package &  &  &  &  &  &  &  & \multicolumn{7}{l|}{\cellcolor[HTML]{C0C0C0}} &  &  &  &  \\ \hline
Generate Coarse-Grain Morphologies &  &  &  &  &  &  &  &  &  &  &  & \multicolumn{5}{l|}{\cellcolor[HTML]{C0C0C0}} &  &  \\ \hline
Evaluate OPV Performance Metrics &  &  &  &  &  &  &  &  &  &  &  &  & \multicolumn{5}{l|}{\cellcolor[HTML]{C0C0C0}} &  \\ \hline
Write Dissertation &  &  &  &  &  &  &  &  &  &  &  &  &  & \multicolumn{5}{l|}{\cellcolor[HTML]{C0C0C0}} \\ \hline
Present Dissertation Defense &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \cellcolor[HTML]{C0C0C0} \\ \hline
\end{tabular}%
}
\caption{Anticipated timeline. * indicates right now, x indicates already accomplished.}
\end{table}
